Hydra Battles in Coq

### 2020-11-02 doc/hydras.tex
removing inefficient eauto with T1

\index{Projects}
\begin{project}
Prove that \texttt{Omega\_plus\_Omega} cannot be a sub-notation of \texttt{Omega}.
\end{project}

@@

\index{Projects}
\begin{project}
 \emph{This exercise is a continuation of Project~\vref{exo:ON-mult}.}
Define an ordinal notation \texttt{Omega2} for $\omega^2=\omega\times\omega$ (using
\texttt{ON\_mult}).

>>>>

\index{Exercises}
\begin{exercise}
Prove that \texttt{Omega\_plus\_Omega} cannot be a sub-notation of \texttt{Omega}.
\end{exercise}

@@

\index{Projects}
\begin{project}
 \emph{This exercise is a continuation of Project~\vref{exo:ON-mult}.}
Use \texttt{ON\_mult} to define an ordinal notation \texttt{Omega2} for $\omega^2=\omega\times\omega$.
